How do changes in ex vary between countries?

### 2022-11-02 draft_working_paper.Rmd
correct code; create tiffs

```{r}
best_breakpoint_model_predictions %>% 
  left_join(country_code_lookup) %>% 
  mutate(country = factor(country, levels = c("England & Wales", "Scotland", "Synthetic Germany", "Spain", "France", "Italy", "Netherlands"))) %>% 
  filter(!is.na(country)) %>% 
  filter(x == 0) %>% 
  group_by(country, sex) %>% 
  arrange(year) %>% 
  mutate(
    ch_ex      = 9 (ex - lag(ex)                 ), 
    ch_ex_pred = 52.25 * (prediction - lag(prediction) )
  ) %>% 
  filter(!is.na(ch_ex), !is.na(ch_ex_pred))  %>% 
  ggplot(aes(year)) + 
  geom_point(aes(y = ch_ex), alpha = 0.35) +
  facet_grid(sex ~ country) +
  geom_hline(yintercept = 0) + 
  geom_line(aes(y = ch_ex_pred), colour = "red") +
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)
  ) + 
  scale_y_continuous(breaks = seq(-30, 50, by = 10)) +
  labs(
    x = "Year",
    y = "Change in life expectancy from previous year (weeks)",
    title = "Predicted and observed annual changes in life expectancy at birth, selected countries",
    subtitle = "Line: Best segmented regression model for the country",
    caption =  "Source: Human Mortality Database. Synthetic Germany based on 20% East/80% West German population weighting"
  )

>>>>

```{r}
best_breakpoint_model_predictions %>% 
  left_join(country_code_lookup) %>% 
  mutate(country = factor(country, levels = c("England & Wales", "Scotland", "Synthetic Germany", "Spain", "France", "Italy", "Netherlands"))) %>% 
  filter(!is.na(country)) %>% 
  filter(x == 0) %>% 
  group_by(country, sex) %>% 
  arrange(year) %>% 
  mutate(
    ch_ex      = 52.25 * (ex - lag(ex)),             
    ch_ex_pred = 52.25 * (prediction - lag(prediction) )
  ) %>% 
  filter(!is.na(ch_ex), !is.na(ch_ex_pred))  %>% 
  ggplot(aes(year)) + 
  geom_point(aes(y = ch_ex), alpha = 0.35) +
  facet_grid(sex ~ country) +
  geom_hline(yintercept = 0) + 
  geom_line(aes(y = ch_ex_pred), colour = "red") +
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)
  ) + 
  scale_y_continuous(breaks = seq(-30, 50, by = 10)) +
  labs(
    x = "Year",
    y = "Change in life expectancy from previous year (weeks)",
    title = "Predicted and observed annual changes in life expectancy at birth, selected countries",
    subtitle = "Line: Best segmented regression model for the country",
    caption =  "Source: Human Mortality Database. Synthetic Germany based on 20% East/80% West German population weighting"
  )
